Tugas UTS

### 2024-02-27 Project/Tugas UTS/Tugas UTS.Rmd
Update

```{r}
raw.data <- read_xlsx("Persentase Penduduk Miskin Menurut Provinsi .xlsx", sheet="R")
data <- raw.data %>% as.data.frame()

@@

```{r}
par(mfrow=c(1,2))
hist(data[,2]); hist(data[,3])
```

```{r}
n <- nrow(data)
#1. Hitung Teta Duga
teta_hat <- mean(data[,2])/ ( mean(data[,2]) +mean(data[,3]) )

#2. Jacknife Sampling
x1 <- matrix(NA, n, n-1)
x2 <- matrix(NA, n, n-1)
for (i in 1:n) {
  x1[i,] <- data[,2][-i]
  x2[i,] <- data[,3][-i]
}
x1bar <- apply(x1, 1, mean)
x2bar <- apply(x2, 1, mean)

@@

```{r}
par(mfrow=c(2,2))
hist(data[,2]); hist(data[,3])
hist(x1); hist(x2)
```

>>>>

```{r}
raw.data <- read.csv("Data PSD.csv")
data <- raw.data[-nrow(raw.data), c("BJR","TL")] %>% as.data.frame()

@@

```{r}
par(mfrow=c(1,2))
hist(data[,1]); hist(data[,2])
```

```{r}
n <- nrow(data)
#1. Hitung Teta Duga
teta_hat <- mean(data[,1])/ ( mean(data[,1]) +mean(data[,2]) )

#2. Jacknife Sampling
x1 <- matrix(NA, n, n-1)
x2 <- matrix(NA, n, n-1)
for (i in 1:n) {
  x1[i,] <- data[,1][-i]
  x2[i,] <- data[,2][-i]
}
x1bar <- apply(x1, 1, mean)
x2bar <- apply(x2, 1, mean)

@@

```{r}
par(mfrow=c(2,2))
hist(data[,1]); hist(data[,2])
hist(x1); hist(x2)
```
